\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits.

% Bridges and pluggable transports are not limited to Tor...

@@

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The obscure strings under ``Connect with provided bridges'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges'', there is a space to paste in
a bridge specification that was obtained out of band.
The ``Help'' button displays instructions on obtaining such
bridge specifications.
}
\label{fig:bridge-options}
\end{figure}

Tor Launcher gives access to a variety of sophisticated
circumvention mechanisms.
Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
interface as it existed at the time we did our study
and lists the available pluggable transports.
Some transports connect directly to a static IP address,
transforming traffic to defeat its on-the-wire identification as Tor;
they rely on the secrecy of their IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which make Tor look like another protocol such as HTTP; and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt Tor to look like random noise.
Other transports do not depend on connecting to a static IP address:
``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
and the three ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks.

@@

\section{Goals/Evaluation Criteria}
\label{sec:goals}
We evaluate the existing and redesigned Tor Browser configuration interface 
through the empirical evaluation and heuristic evaluation criteria below.

@@

\begin{enumerate}
    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing. 
    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
\end{enumerate}

@@

\begin{enumerate}
    \item {\bfseries Task Completion}: Almost all can successfully connect to Tor
    \item {\bfseries  Time to Completion}: Time to completion. 
    \item {\bfseries Safe for High-Risk Users}: It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
\end{enumerate}

>>>>

@@

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The obscure strings under ``Connect with provided bridges'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges'', there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines.
}
\label{fig:bridge-options}
\end{figure}

Tor Launcher gives access to a variety of sophisticated
circumvention mechanisms.
Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
interface as it existed at the time we did our study
and lists the available pluggable transports.
Some transports connect directly to a static IP address,
obfuscating traffic to defeat on-the-wire identification;
they rely on the secrecy of their IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which make Tor look like another protocol such as HTTP; and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt Tor to look like random noise.
Other transports work differently and do not depend on connecting to a static IP address:
``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
and the three ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks.

@@

\section{Goals/Evaluation Criteria}
\label{sec:goals}
In the course of our experiments we evaluated two versions
of the Tor Launcher interface.
The first, which we have labeled ``OLD'' in figures and tables,
is the version that is being distributed to users now.
The second, ``NEW'', is the prototype we revised and redesigned
in order to provide better usability.
We evaluate the old and new interfaces
through the empirical evaluation and heuristic evaluation criteria below.

@@

\begin{enumerate}
    \item  {\bfseries Visibility of system status}: Provide feedback on what the system is doing. 
    \item  {\bfseries Error management}: Expressing errors in plain language and offering a solution. 
    \item  {\bfseries Understandable language}: Explaining the task, rather than technical concepts. 
    \item  {\bfseries Simple design}: Showing options on an as-needed basis. 
\end{enumerate}

@@

\begin{enumerate}
    \item {\bfseries Task completion rate}: Almost all can successfully connect to Tor.
    \item {\bfseries  Time to completion}: Measured between program startup and successful connection to Tor.
    \item {\bfseries Safety for high-risk users}: It should be possible to configure Tor without leaking the fact that the user is using Tor. 
\end{enumerate}
